%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage{fontspec}
\newfontfamily{\AIfont}{academicons.ttf}[Path=./]
\providecolor{googlescholar}{named}{color1}
\providecommand*{\googlescholarsocialsymbol}{}
\renewcommand*{\googlescholarsocialsymbol}{{\color{googlescholar}\small{\AIfont\symbol{"E9D4}}}~}


% Use filled bullet points instead of hollow circles
\renewcommand{\labelitemi}{\textbullet}

% Smaller name and title in header
\renewcommand*{\namefont}{\fontsize{24}{26}\mdseries\upshape}
\renewcommand*{\titlefont}{\Large\mdseries\slshape}

% Redefine cventry to put dates and location on the right
\renewcommand*{\cventry}[7][.25em]{%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}%
    {\bfseries #4} & {\itshape\color{color1} #5} \\%
    {\small\scshape #3} & {\small\color{gray} #2} \\%
  \end{tabular*}%
  \ifx&#7&%
  \else{\\\vbox{\small #7}}\fi%
  \par\addvspace{0.6em}}

\usepackage[scale=0.88]{geometry}

% Small hints column just for section title bars
\setlength{\hintscolumnwidth}{0cm}

% Override section to show a fixed-width blue bar
\makeatletter
\RenewDocumentCommand{\section}{sm}{%
  \par\addvspace{2.5ex}%
  \phantomsection{}%
  \addcontentsline{toc}{section}{#2}%
  \noindent\raisebox{0.2ex}{\color{color1}\rule{1.8cm}{0.95ex}}\hspace{0.5em}{\sectionstyle{#2}}%
  \par\nobreak\addvspace{1ex}\@afterheading}
\makeatother

% Bibliography
\usepackage[backend=biber, style=numeric, sorting=ydnt, maxbibnames=99, url=false, isbn=false, eprint=false, doi=false, giveninits=true, defernumbers=true]{biblatex}
\addbibresource{publications.bib}

% Name format: I. Family with bold for highlighted authors
\DeclareNameAlias{default}{given-family}
\renewcommand*{\mkbibnamegiven}[1]{%
  \ifitemannotation{highlight}{\textbf{#1}}{#1}}
\renewcommand*{\mkbibnamefamily}[1]{%
  \ifitemannotation{highlight}{\textbf{#1}}{#1}}

% Make all hyperlinks blue (run after moderncv's own hypersetup)
\AtEndPreamble{%
  \hypersetup{colorlinks=true, urlcolor=color1, linkcolor=color1, citecolor=color1}}

% Title format: quoted with hyperlink
\DeclareFieldFormat[inproceedings,misc]{title}{%
  \iffieldundef{url}{\mkbibquote{#1}}{\href{\thefield{url}}{\mkbibquote{#1}}}}

% "In" before venue for inproceedings only (no "In:" for misc)
\renewbibmacro{in:}{\ifentrytype{inproceedings}{\printtext{\bibstring{in}\intitlepunct}}{}}

% Note format: soft red for awards/distinctions in conference papers
\definecolor{awardred}{HTML}{C0392B}
\DeclareFieldFormat[inproceedings]{note}{{\color{awardred}#1}}



% Personal data
\name{Edoardo}{Debenedetti}
\title{Research Scientist at AI Sequrity Company}
\phone[mobile]{(+41) 76 699 43 27}
\email{edebenedetti@inf.ethz.ch}
\homepage{edoardo.science}
\social[github]{dedeswim}
\social[googlescholar][scholar.google.com/citations?user=6Urve9wAAAAJ]{Edoardo Debenedetti}

\begin{document}

\makecvtitle

%-------------------------------------------------------------------------------
% Education
%-------------------------------------------------------------------------------
\section{Education}

\cventry{08/2022 -- Q2/2026 (exp.)}{PhD in Computer Science}{ETH Z{\"u}rich -- Federal Institute of Technology Z{\"u}rich}{Z{\"u}rich, Switzerland}{}{%
\begin{itemize}
  \item Focus: \textbf{Real-world machine learning security and privacy}, advised by \textbf{Prof. Florian Tram\`{e}r} in the \textbf{SPY Lab}.
  \item \textbf{IT Coordinator} for the group: managing the GPU servers and hardware resources.
\end{itemize}}

\cventry{09/2019 -- 04/2022}{MSc in Computer Science}{EPFL -- Federal Institute of Technology Lausanne}{Lausanne, Switzerland}{}{%
\begin{itemize}
  \item \textbf{GPA 5.63/6}, focus on \textbf{Machine Learning, Security, and Privacy}.
  \item Thesis: \textit{A Light Recipe to Train Robust Vision Transformers}, supervised by \textbf{Prof. Prateek Mittal} (Princeton).
\end{itemize}}

\cventry{09/2016 -- 07/2019}{BSc in Computer Engineering}{Politecnico di Torino}{Turin, Italy}{}{%
\begin{itemize}
  \item \textbf{GPA 28.4/30}, graduation mark 110/110, \textbf{top 9\%}.
  \item \textbf{Exchange year at Tongji University}, in Shanghai (China).
\end{itemize}}

%-------------------------------------------------------------------------------
% Industry experience
%-------------------------------------------------------------------------------
\section{Industry experience}

\cventry{02/2026 -- present}{Research Scientist}{AI Sequrity Company}{Zurich, Switzerland}{}{%
Working on AI agents security.}

\cventry{07/2025 -- 11/2025}{Research Scientist Intern}{Meta}{Menlo Park, CA, United States}{}{%
Worked on AI agents security evaluations in the GenAI Red Team.}

\cventry{10/2024 -- 02/2025}{Student Researcher}{Google}{Munich, Germany -- Zurich, Switzerland}{}{%
\begin{itemize}
  \item Worked on CaMeL, a system level defense against prompt injection attacks, to build secure AI agents.
  \item Co-hosted by Tianqi Fan (Google ML Red Team) and Ilia Shumailov (Google DeepMind).
\end{itemize}}

\cventry{07/2021 -- 09/2021}{Software Engineering Intern}{Bloomberg LP}{London, United Kingdom}{}{%
\begin{itemize}
  \item Worked in the \textbf{Multi Asset Risk System} team, on the re-design and implementation of the configuration of a distributed logging library.
  \item Move the configuration of a \textbf{distributed logging library} from an internal technology to a \textbf{centralized SQL DB}, using a \textbf{cache} and a \textbf{C++ service}.
  \item The configuration is checked \textbf{\textasciitilde 1M times per minute}, and the usage of the cache gave a \textbf{\textasciitilde 23x speed improvement} w.r.t. querying the DB.
\end{itemize}}

\cventry{08/2020 -- 01/2021}{Research Intern}{Armasuisse Cyber-Defence Campus}{Lausanne, Switzerland}{}{%
\begin{itemize}
  \item Worked on \textbf{Machine Unlearning} and \textbf{Membership Inference Attacks} against Generative Models, supervised by \textbf{Prof. Mathias Humbert}.
  \item Adapt the \textbf{MIA} technique proposed by the \textit{GAN-Leaks} work (by Chen et al.), to work after the removal some datapoints from the training set.
  \item The technique achieved \textbf{promising results} when attacking DCGAN trained on the CelebA dataset.
\end{itemize}}

%-------------------------------------------------------------------------------
% Publications
%-------------------------------------------------------------------------------
\section{Publications}


\nocite{*}

{\large\textsc{Conference Proceedings}}\par\vspace{2mm}
\newrefcontext[labelprefix={C}]
\printbibliography[heading=none, keyword=conference, resetnumbers=true]

\vspace{2mm}
{\large\textsc{Workshop Papers}}\par\vspace{2mm}
\newrefcontext[labelprefix={W}]
\printbibliography[heading=none, keyword=workshop, resetnumbers=true]

\vspace{2mm}
{\large\textsc{Manuscripts}}\par\vspace{2mm}
\newrefcontext[labelprefix={M}]
\printbibliography[heading=none, keyword=manuscript, resetnumbers=true]

%-------------------------------------------------------------------------------
% Honors and Awards
%-------------------------------------------------------------------------------
\section{Honors and Awards}

\cvlistitem{\textbf{SafeBench First Prize}, 50'000 USD prize for the AgentDojo Benchmark, 2025.}
\cvlistitem{\textbf{Oral Acceptance --- ICML 2025}, Top 0.98\% of submitted papers, 2025.}
\cvlistitem{\textbf{Spotlight Acceptance --- NeurIPS 2024 Datasets and Benchmarks Track}, Top 4\% of submitted papers, 2024.}
\cvlistitem{\textbf{Distinguished Paper Award Runner-up --- IEEE SaTML}, Top 1\% of submitted papers, 2024.}
\cvlistitem{\textbf{Oral presentation --- ICML AdvML Frontiers Workshop}, Top 10\% accepted papers, 2023.}
\cvlistitem{\textbf{CYD Doctoral Fellowship}, full PhD funding for 4 years, worth \textbf{USD 536'000} (CHF 461'000), from Armasuisse CYD Campus and EPFL. Only used for $\sim$1.5 years, 2023.}
\cvlistitem{\textbf{Google TPU Research Cloud Program}, extensive \textbf{hardware support for 8 months} to work on the Master's Thesis, 2021.}
\cvlistitem{\textbf{Best Paper Honorable Mention --- ICLR Workshop on Security and Safety in ML Systems}, top 2 out of 50 accepted papers, 2021.}

%-------------------------------------------------------------------------------
% Invited talks
%-------------------------------------------------------------------------------
\section{Invited talks}

\cvlistitem{\textbf{UC Berkeley EECS Security Seminar.} -- \textit{Defeating Prompt Injections by Design.}, 2025.}
\cvlistitem{\textbf{armasuisse Cyber-Alp Retreat.} -- \textit{Defeating Prompt Injections by Design.}, 2025.}
\cvlistitem{\textbf{ICLR Workshop on Building Trust in LLMs and LLM Applications.} -- \textit{Evaluating and Defending against Prompt Injection Attacks}, 2025.}
\cvlistitem{\textbf{UMass AI Security and Privacy Seminar} -- \textit{Defeating Prompt Injections by Design}, 2025.}
\cvlistitem{\textbf{Google AE Summit} -- \textit{Prompt Injection Attacks: A Critical Risk for Deployed AI Agents}, 2025.}
\cvlistitem{\textbf{Google} -- \textit{Defeating Prompt Injections by Design}, 2025.}
\cvlistitem{\textbf{Google} -- \textit{AgentDojo: A Dynamic Environment to Evaluate Attacks and Defenses for LLM Agents}, 2024.}
\cvlistitem{\textbf{Princeton Language and Intelligence} -- \textit{AgentDojo: A Dynamic Environment to Evaluate Attacks and Defenses for LLM Agents}, 2024.}
\cvlistitem{\textbf{armasuisse Cyber-Alp Retreat} -- \textit{Evading Black-box Classifiers Without Breaking Eggs}, 2024.}
\cvlistitem{\textbf{ACL SIGSEC} -- \textit{Privacy Side-channels in Machine Learning Systems}, 2023.}
\cvlistitem{\textbf{TU Graz EfficientML Reading Group} -- \textit{Privacy Side-channels in Machine Learning Systems}, 2023.}

%-------------------------------------------------------------------------------
% Press coverage
%-------------------------------------------------------------------------------
\section{Press coverage}

\cvlistitem{\textbf{The Economist} -- \textit{\href{https://www.economist.com/science-and-technology/2025/09/22/why-ai-systems-might-never-be-secure}{``Why AI systems might never be secure''}}, September 2025.}
\cvlistitem{\textbf{Ars Technica} -- \textit{\href{https://arstechnica.com/information-technology/2025/04/researchers-claim-breakthrough-in-fight-against-ais-frustrating-security-hole/}{``Researchers claim breakthrough in fight against AI's frustrating security hole''}}, April 2025.}
\cvlistitem{\textbf{MIT Technology Review} -- \textit{\href{https://www.technologyreview.com/2025/04/04/1114228/cyberattacks-by-ai-agents-are-coming/}{``Cyberattacks by AI agents are coming''}}, April 2025.}

%-------------------------------------------------------------------------------
% Teaching
%-------------------------------------------------------------------------------
\section{Teaching}

\cvlistitem{\textbf{Privacy Enhancing Technologies} -- ETH Z{\"u}rich: 2024 (Teaching Assistant)}
\cvlistitem{\textbf{Information Security Lab} -- ETH Z{\"u}rich: 2022, 2023 (Teaching Assistant)}
\cvlistitem{\textbf{Large Language Models} -- ETH Z{\"u}rich: 2023, 2024, 2025 (Teaching Assistant)}

%-------------------------------------------------------------------------------
% Professional Service
%-------------------------------------------------------------------------------
\section{Professional Service}

\subsection{Reviewer}
\cvlistitem{\textbf{ICLR}: 2025}
\cvlistitem{\textbf{NeurIPS}: 2024, 2025}
\cvlistitem{\textbf{NeurIPS Datasets and Benchmarks Track}: 2022, 2023, 2024}
\cvlistitem{\textbf{CCS AISec workshop}: 2023, 2024}

\subsection{Conference service}
\cvlistitem{\textbf{Competition organizer at SaTML 2024}: lead organizer of the \href{https://ctf.spylab.ai}{\textit{Large Language Models Capture-the-Flag}}. More than \textbf{400 users and 140 teams} signed up and more than 70 defenses were submitted. The competition report was accepted at NeurIPS 2024 and awarded a spotlight.}
\cvlistitem{\textbf{Volunteer at NeurIPS 2021}: helped with monitoring the website and technical issues.}

\subsection{Open Source Maintainer}
\cvlistitem{\textbf{AgentDojo}: Benchmark for Prompt Injection Attacks and Defenses.
  \begin{itemize}
    \item Lead the development of the environment and wrote the documentation.
    \item \textbf{239 stars} (measured in August 2025).
  \end{itemize}
  Repository at \url{https://github.com/ethz-spylab/agentdojo}.}

\vspace{1em}
\begin{center}
  \small{Last update \today.}
\end{center}

\end{document}
