%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {MSc in Computer Science} % Degree
  {EPFL - Federal Institute of Technology Lausanne} % Institution
  {Lausanne, Switzerland} % Location
  {Sep. 2019 - Apr. 2022 (Expected)} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item \textbf{GPA 5.51/6}, focus on \textbf{Machine Learning $\cap$ Security $\cap$ Privacy}.
      \item Working on my Master's Thesis about the robustness of Vision Transformers at \textbf{Princeton University}, in \textbf{Prof. Mittal}'s lab.
      \item Worked on \textbf{RobustBench}, a standardized benchmark for \textbf{Adversarial Robustness} at \textbf{Prof. Flammarion}'s TML Lab.
      \item Worked on a \textbf{research} project about \textbf{deepfakes} counteraction via influence functions at \textbf{Prof. Troncoso}'s SPRING Lab.
    \end{cvitems}
  }
  \cventry
  {BSc in Computer Engineering} % Degree
  {Politecnico di Torino} % Institution
  {Turin, Italy} % Location
  {Sep. 2016 - Jul. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item \textbf{GPA 28.4/30}, graduation mark 110/110, \textbf{top 9\%}.
      \item \textbf{Exchange year at 同济大学} (Tongji University), in Shanghai (China), supported by a \textbf{full scholarship} granted to the top 31\% applicants. \vspace{0.2cm}
    \end{cvitems}
  }
  \cventry
  {High School Diploma} % Degree
  {Navy Military College ``F. Morosini"} % Institution
  {Venice, Italy} % Location
  {Sep. 2013 - Jul. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item Selected to lead sophomores as \textbf{prefect} during my final year.
      \item \textbf{Military training} on Italian Navy's Ships and at Italian Navy's Marine Corps.
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
