%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
\cventry
  {Research Scientist} % Job title
  {AI Sequrity Company} % Organization
  {Zurich, Switzerland} % Location
  {02/2026 - present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Working on AI agents security.
    \end{cvitems}
  }

\cventry
  {Research Scientist Intern} % Job title
  {Meta} % Organization
  {Menlo Park, CA, United States} % Location
  {07/2025 - 11/2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Worked on AI agents security evaluations in the GenAI Red Team.
    \end{cvitems}
  }

\cventry
  {Student Researcher} % Job title
  {Google} % Organization
  {Munich, Germany -- Zurich, Switzerland} % Location
  {10/2024 - 02/2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Worked on CaMeL, a system level defense against prompt injection attacks, to build secure AI agents.
      \item Co-hosted by Tianqi Fan (Google ML Red Team) and Ilia Shumailov (Google DeepMind).
    \end{cvitems}
  }
  
  \cventry
  {Software Engineering Intern} % Job title
  {Bloomberg LP} % Organization
  {London, United Kingdom} % Location
  {07/2021 - 09/2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Worked in the \textbf{Multi Asset Risk System} team, on the re-design and implementation of the configuration of a distributed logging library.
      \item Move the configuration of a \textbf{distributed logging library} from an internal technology to a \textbf{centralized SQL DB}, using a \textbf{cache} and a \textbf{C++ service}.
      % \item Used  to fetch the configuration and serve it to the client library.
      \item The configuration is checked \textbf{\textasciitilde 1M times per minute}, and the usage of the cache gave a \textbf{\textasciitilde 23x speed improvement} w.r.t. querying the DB.
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Research Intern} % Job title
  {Armasuisse Cyber-Defence Campus} % Organization
  {Lausanne, Switzerland} % Location
  {08/2020 - 01/2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Worked on \textbf{Machine Unlearning} and \textbf{Membership Inference Attacks} against Generative Models, supervised by \textbf{Prof. Mathias Humbert}.
      \item Adapt the \textbf{MIA} technique proposed by the \textit{GAN-Leaks} work (by Chen et al.), to work after the removal some datapoints from the training set.
      \item The technique achieved \textbf{promising results} when attacking DCGAN trained on the CelebA dataset
    \end{cvitems}
  }

  %---------------------------------------------------------
  % \cventry
  % {Software Engineering Intern} % Job title
  % {Reply} % Organization
  % {Turin, Italy} % Location
  % {Nov. 2018 - Feb. 2019} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item Developed a \textbf{chatbot} that answers questions about GDPR law, using \textbf{TypeScript}, \textbf{Redis}, % \textbf{MongoDB}, \textbf{IBM Watson Assistant}, and \textbf{Docker}.
  %     \item Worked with \textbf{RPA}, using \textbf{Python}. One of the bots \textbf{decreased a task duration by 88\%,} without requiring % human intervention.
  %   \end{cvitems}
  % }

\end{cventries}
