%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsection{Publications}
\descriptionstyle{$^*$ denotes equal contribution.}

\cventry
{Conference proceedings} % type of publication
{} % leave mpty!
{} % leave mpty!
{} % leave mpty!
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Debenedetti, E.}, Shumailov, I., Fan, T., Hayes, J., Carlini, N., Fabian, D., Kern, C., Shi, C., Terzis, A., Tramèr, F., \textit{\href{https://arxiv.org/abs/2503.18813}{``Defeating Prompt Injections by Design''}}, 4th IEEE Conference on Secure and Trustworthy Machine Learning, 2026.
        \item Carlini, N., Rando, J., \textbf{Debenedetti, E.}, Nasr, M., Tramèr, F., \textit{\href{https://arxiv.org/abs/2503.01811}{``AutoAdvExBench: Benchmarking Autonomous Exploitation of Adversarial Example Defenses''}}, Forty-Second International Conference on Machine Learning, 2025, \textbf{Oral}.
        \item Aerni, M., Rando, J., \textbf{Debenedetti, E.}, Carlini, N., Ippolito, D. Tramèr, F., \textit{\href{https://arxiv.org/abs/2411.10242}{``Measuring Non-Adversarial Reproduction of Training Data in Large Language Models''}}, Thirteenth International Conference on Learning Representations, 2025.
        \item Nestaas, F., \textbf{Debenedetti, E.}, Tramèr, F., \textit{\href{https://arxiv.org/abs/2406.18382}{``Adversarial Search Engine Optimization for Large Language Models"}}, Thirteenth International Conference on Learning Representations, 2025.
        \item\textbf{Debenedetti, E.}, Zhang, J., Balunovi\'c, M., Beurer-Kellner, L., Fischer, M. Tramèr, F., \textit{\href{https://arxiv.org/abs/2406.13352}{``AgentDojo: A Dynamic Environment to Evaluate Attacks and Defenses for LLM Agents"}}, Thirty‑eighth Conference on Neural Information Processing Systems Datasets and Benchmarks Track, 2024. (\textbf{SafeBench First Prize}).
        \item\textbf{Debenedetti, E.$^*$}, Rando, J.$^*$, Paleka, D.$^*$, Silaghi, F., Albastroiu, D., Cohen, N., Lemberg, Y., Ghosh, R., Wen, R., Salem, A., Cherubin, G., Zanella-Beguelin, S., Schmid, R., Klemm, V., Miki, T., Li, C. Kraft, S., Fritz, M., Tramèr, F., Abdelnabi, S., Schönherr, L. \textit{\href{https://arxiv.org/abs/2406.07954}{``Dataset and Lessons Learned from the 2024 SaTML
    LLM Capture-the-Flag Competition"}}, Thirty‑eighth Conference on Neural Information Processing Systems Datasets and Benchmarks Track, 2024 (\textbf{Spotlight}).
        \item Chao, P.$^*$, \textbf{Debenedetti, E.$^*$}, Robey, A.$^*$, Andriushchenko, M.$^*$, Croce, F., Sehwag, V., Dobriban, E., Flammarion, N., Pappas, G., Tramèr, F, Hassani, H., Wong, E., \textit{\href{https://arxiv.org/abs/2404.01318}{``JailbreakBench: An Open Robustness Benchmark for Jailbreaking Language Models"}}, Thirty‑eighth Conference on Neural Information Processing Systems Datasets and Benchmarks Track, 2024.
        \item \textbf{Debenedetti, E.}, Severi, G., Carlini, N., Choquette-Choo, C. A., Jagielski, M., Nasr, M., Wallace, E., Tramèr, F., \textit{\href{https://arxiv.org/abs/2309.05610}{``Privacy Side Channels in Machine Learning Systems"}}, 33rd USENIX Security Symposium, 2024.
        \item \textbf{Debenedetti, E.}, Carlini, N., Tram{\`e}r, F., \textit{\href{https://arxiv.org/abs/2306.02895}{``Evading Black-box Classifiers Without Breaking Eggs''}}, 2nd IEEE Conference on Secure and Trustworthy Machine Learning, 2024, \textbf{Distinguished Paper Award Runner-up}.
        \item \textbf{Debenedetti, E.}, Sehwag, V., Mittal, P., \textit{\href{https://arxiv.org/abs/2209.07399}{``A Light Recipe to Train Robust Vision Transformers''}}, 1st IEEE Conference on Secure and Trustworthy Machine Learning, 2023.
        \item Croce, F.$^*$, Andriushchenko, M.$^*$, Sehwag, V.$^*$, \textbf{Debenedetti, E.$^*$}, Flammarion, N., Chiang, M., Mittal, P., Hein, M., \textit{\href{https://arxiv.org/abs/2010.09670}{``RobustBench: a standardized adversarial robustness benchmark''}}, Thirty‑fifth Conference on Neural Information Processing Systems Datasets and Benchmarks Track, 2021.
    \end{cvitems}
}

\cventry
{Workshop papers} % type of publication
{} % leave mpty!
{} % leave mpty!
{} % leave mpty!
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item  Freeman, J., Rippe, C., \textbf{Debenedetti, E.}, Andriushchenko, M., \textit{\href{}{``Exploring Memorization and Copyright Violation in Frontier LLMs: A Study of the New York Times v. OpenAI 2023 Lawsuit"}}, NeurIPS Safe Generative AI Workshop, 2024.
    \item \textbf{Debenedetti, E.}, Wan, Z., Andriushchenko, M., Sehwag, V., Bhardwaj, K, Kailkhura, B., \textit{\href{https://arxiv.org/abs/2312.13131}{``Scaling Compute Is Not All You Need for Adversarial Robustness"}}, ICLR Workshop on Reliable and Responsible Foundation Models, 2024.
    \end{cvitems}
}

\cventry
{Manuscripts} % type of publication
{} % leave mpty!
{} % leave mpty!
{} % leave mpty!
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Beurer-Kellner, L., Buesser, B., Creţu, A., \textbf{Debenedetti, E.}, Dobos, D., Fabian, D., Fischer, M., Froelicher, D., Grosse, K., Naeff, D., Ozoani, E., Paverd, E., Tramèr, F, Volhejn, V., \textit{\href{https://arxiv.org/abs/2506.08837}{``Design Patterns for Securing LLM Agents against Prompt Injections''}}, arXiv ePrint 2506.08837, 2025 ($\alpha\beta$ order).
    \item Carlini, N., Nasr, M., \textbf{Debenedetti, E.}, Wang, B., Choquette-Choo C., Ippolito, D., Tramèr, F., Jagielski, M., \textit{\href{https://arxiv.org/abs/2505.11449}{``LLMs unlock new paths to monetizing exploits''}}, arXiv ePrint 2505.11449, 2025.
    \item Qi, X., Huang, Y., Zeng, Y., \textbf{Debenedetti, E.}, Geiping, J., He, L., Huang, K., Madhushani Sehwag, U., Sehwag, V., Shi, W., Wei, B., Xie, T., Chen, D., Chen, P., Ding, J., Jia, R., Ma, J., Narayanan, A., Su, W., Wang, M., Xiao, C., Li, B., Song, D., Henderson, P., Mittal, P., \textit{\href{https://arxiv.org/abs/2405.19524}{``AI Risk Management Should Incorporate Both Safety and Security"}}, arXiv ePrint 2405.19524, 2024.
    \end{cvitems}
}
