\cvsection{Invited talks}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
\vspace{5.0mm}
\begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item{\textbf{UC Berkeley EECS Security Seminar.} -- \textit{Defeating Prompt Injections by Design.}, 2025.}
    \item{\textbf{armasuisse Cyber-Alp Retreat.} -- \textit{Defeating Prompt Injections by Design.}, 2025.}
    \item{\textbf{ICLR Workshop on Building Trust in LLMs and LLM Applications.} -- \textit{Evaluating and Defending against Prompt Injection Attacks}, 2025.}
    \item{\textbf{UMass AI Security and Privacy Seminar} -- \textit{Defeating Prompt Injections by Design}, 2025.}
    \item{\textbf{Google AE Summit} -- \textit{Prompt Injection Attacks: A Critical Risk for Deployed AI Agents}, 2025.}
    \item{\textbf{Google} -- \textit{Defeating Prompt Injections by Design}, 2025.}
    \item{\textbf{Google} -- \textit{AgentDojo: A Dynamic Environment to Evaluate Attacks and Defenses for LLM Agents}, 2024.}
    \item{\textbf{Princeton Language and Intelligence} -- \textit{AgentDojo: A Dynamic Environment to Evaluate Attacks and Defenses for LLM Agents}, 2024.}
    \item{\textbf{armasuisse Cyber-Alp Retreat} -- \textit{Evading Black-box Classifiers Without Breaking Eggs}, 2024.}
    \item{\textbf{ACL SIGSEC} -- \textit{Privacy Side-channels in Machine Learning Systems}, 2023.}
    \item{\textbf{TU Graz EfficientML Reading Group} -- \textit{Privacy Side-channels in Machine Learning Systems}, 2023.}
\end{cvitems}
\end{cvparagraph}